Benchmarks of the Non-Relativistic Hydrodynamics Algorithms in \thornado

### 2017-01-30 Documents/Euler/Benchmarks1D/draft.tex
Captions for Sod figures.

First, the tests were run with values computed at different intervals; the method of integration is the same in each test. Between the two endpoints, 128, 256, 512, and 1024 points were computed for on each respective test. Figures~\ref{fig:dencellcomp_20}--\ref{fig:pvcellcomp} show results of these tests:
\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=.95\textwidth]{dencellcomp_20}
  \end{center}
  \caption{density}
  \label{fig:dencellcomp_20}
\end{figure}
%\newpage

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prscellcomp_20} &
	  \includegraphics[width=.425\textwidth]{velcellcomp_20}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
  \label{fig:pvcellcomp}
\end{figure}
%\newpage

>>>>

First, the tests were run with values computed at different intervals; the method of integration is the same in each test. Between the two endpoints, 128, 256, 512, and 1024 points were computed for on each respective test. Figures~\ref{fig:dencellcomp_20}--\ref{fig:pvcellcomp} show results of these tests:
\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=.95\textwidth]{dencellcomp_20}
  \end{center}
  \caption{Results showing the density for Sod's shock tube at $t=0.2$, computed with the first-order method using different number of elements: 128 (solid red), 256 (dashed green), 512 (dotted blue), and 1024 (dash-dot pink).  The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted cyan line.}
  \label{fig:dencellcomp_20}
\end{figure}
%\newpage

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{velcellcomp_20} &
      \includegraphics[width=.475\textwidth]{prscellcomp_20}
    \end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:dencellcomp_20}:
  velocity (left panel) and pressure (right panel).}
  \label{fig:pvcellcomp}
\end{figure}
%\newpage
